### 2025-08-02 correlation.qmd
20250801 - correlation matrix plots
20250802 - degrees of freedom

The $r$ value (`{r} petersenlab::apa(pearson_r, decimals = 2, leading = FALSE)`) is slightly negative.
The [effect size](#sec-practicalSignificance) of the association is small—for what is considered a small, medium, and large effect size for $r$ values, see @sec-effectSizeThresholds.
The $p$-value is less than .05, so it is a statistically significant correlation.
We could report this finding as follows: There was a statistically significant, weak negative association between height and fantasy points ($r(`r pearson_df`) = `r petersenlab::apa(pearson_r, decimals = 2, leading = FALSE)`$, $p `r petersenlab::pValue(pearson_p)`$); the taller a player was, the fewer fantasy points they tended to score.

@@

GGally::ggcorr(player_stats_seasonal[,c("height","weight","fantasyPoints")])
```

>>>>

The $r$ value (`{r} petersenlab::apa(pearson_r, decimals = 2, leading = FALSE)`) is slightly negative.
The [effect size](#sec-practicalSignificance) of the association is small—for what is considered a small, medium, and large effect size for $r$ values, see @sec-effectSizeThresholds.
The number of degrees of freedom ($df$) for a statistical test of a correlation coefficient is in @eq-correlationDF.
The $p$-value is less than .05, so it is a statistically significant correlation.
We could report this finding as follows: There was a statistically significant, weak negative association between height and fantasy points ($r(`r pearson_df`) = `r petersenlab::apa(pearson_r, decimals = 2, leading = FALSE)`$, $p `r petersenlab::pValue(pearson_p)`$); the taller a player was, the fewer fantasy points they tended to score.

$$
df = n - 2
$$ {#eq-correlationDF}

@@

GGally::ggcorr(
  player_stats_seasonal[,c("height","weight","fantasyPoints")],
  label = TRUE,
  label_round = 2)
```
